Limits to Ecological Forecasting: Estimating Uncertainty for Critical Transitions with Deep Learning

### 2022-09-22 manuscript/manuscript.Rmd
Making sure not forgetting anything here

We examine forecast skill for each of the six forecasting methods (MCMC, ARIMA, block-RNN, GRU, LSTM, and Transformer) in each of our three scenarios (Hopf bifurcation, saddle-node bifurcation, and stochastic transition).
In addition to these cases, we also consider an "ensemble model", generated by drawing from the distribution of all models except the MCMC model. 
Such ensemble techniques can better reflect uncertainty than relying on any single method [@gneiting_weather_2005].
For simplicity, we consider the unweighted case, where each model is represented equally in the ensemble.
Using model-based simulations allows us to examine performance against multiple (n=100) replicates of the "true" process, which further helps identify differences that may occur solely due to chance. 
By taking the true model structure as given, MCMC methods can be used to determine a theoretical limit of forecasting skill.
Note that in both bifurcation scenarios, future dynamics will visit states never previously observed in the historical data that was used to train each of the methods (e.g. very small population sizes). 
This no-analog aspect of forecasting bifurcation dynamics means that even with many sample points in the training data _and_ perfect knowledge of the true model structure, posterior distributions of parameter values are still influenced by the choice of priors.

>>>>

We examine forecast skill for each of the six forecasting methods (MCMC, ARIMA, block-RNN, GRU, LSTM, and Transformer) in each of our three scenarios (Hopf bifurcation, saddle-node bifurcation, and stochastic transition).
In addition to these cases, we also consider an "ensemble model", generated by drawing from the distribution of all models except the MCMC model -- throughout our figures, this ensemble model is denoted by "ml_ensemble". 
Such ensemble techniques can better reflect uncertainty than relying on any single method [@gneiting_weather_2005].
For simplicity, we consider the unweighted case, where each model is represented equally in the ensemble.
Using model-based simulations allows us to examine performance against multiple (n=100) replicates of the "true" process, which further helps identify differences that may occur solely due to chance. 
By taking the true model structure as given, MCMC methods can be used to determine a theoretical limit of forecasting skill.
Note that in both bifurcation scenarios, future dynamics will visit states never previously observed in the historical data that was used to train each of the methods (e.g. very small population sizes). 
This no-analog aspect of forecasting bifurcation dynamics means that even with many sample points in the training data _and_ perfect knowledge of the true model structure, posterior distributions of parameter values are still influenced by the choice of priors.
